Using cosmic variance to constrain the dark matter halo mass of Lyman-alpha emitting galaxies at $z$=3.1

### 2013-03-30 paper/ms.tex
text added to the correlation fuction section

We calculate the mean angular correlation function (ACF) for the best
models for a mock survey using the match and random methods with 
two different surface areas: $1)$ the full survey (12 subfields) and
$2)$  e SSA22 field (7 subfields) reported by Yamada et al 2012 
(see section XX) . The results for these calculations  are shown 
in figure \ref{figure:correlation_match} (match) and figure
\ref{figure:correlation_random} (random).  The error bars in these figure
represent the standard deviation of the ACF over the subfields.

We compare these results with the observed ACF in the SSA22 field reported by Hayashino et al. 2004 .

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/match_full_correlation_selected_models.pdf}
\hspace{5mm}
\includegraphics[width=0.46\linewidth,angle=0]{./plot/match_large_correlation_selected_models.pdf}\\
\end{center} 
\caption{ mean ACFs over the 7 subfields of the SSA22 field and their correponding standard deviation (error bars)
some selected models in different mass ranges. \label{figure:correlation_match} }

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/random_full_correlation_selected_models.pdf}
\hspace{5mm}
\includegraphics[width=0.46\linewidth,angle=0]{./plot/random_large_correlation_selected_models.pdf}\\
\end{center} 
\caption{ mean ACFs over the 7 subfields of the SSA22 field and their correponding standard deviation (error bars)
some selected models in different mass ranges. \label{figure:correlation_match} }

>>>>

As a prediction, we calculate the mean angular correlation function (ACF) for some of the best
models for a mock survey using the match and random methods with 
two different surface areas: $1)$ the full survey (12 subfields) and
$2)$  e SSA22 field (7 subfields) reported by Yamada et al 2012 
(see section XX) . The results for these calculations  are shown 
in figure \ref{figure:correlation_match} (match) and figure
\ref{figure:correlation_random} (random).  The error bars in these figures
represent the standard deviation of the ACF over the subfields. 
We compare these results with the observed ACF in a field of the the SSA22 region
reported by Hayashino et al in 2004.

We can generally observe that the standard deviation of the computed ACF 
in the subfields increase when  increasing $M_{min}$ following the same 
trend as in figure \ref{figure:laes_dist}.Therefore, as the cosmic variance
increase when increasing the halos mass the increment in the ACF standard 
deviation when increasing $M_{min}$ is a direct consequence of cosmic variance.

Given that the ACF reported by Hayashino et al en 2004 is taken over the densest 
field oserved in the SSA22 region by  Yamada et el in 2012 it is expected that
the predicted ACF in the SSA22 region should reproduce this observation. In the 
left panel of figure \ref{figure:correlation_match} we can see the predicted ACFs 
an their corresponding standard deviation over the seven fields that mock the SSA22 
region. It can be seen that the model with $M_min=10.6$ seems to better reproduce the 
Hayashino's ACF and that the corresponding field is in fact an overdense field in the
SSA22 region covered by Yamada et al.

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/match_large_correlation_selected_models.pdf}
\hspace{5mm}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/match_full_correlation_selected_models.pdf}
\end{center} f
\caption{ mean ACFs   and their correponding standard deviation (error bars)  of some selected models in different mass ranges
over the 7 subfields of the SSA22 field (left) and the entire 12 field sample (rigth) using the
match configuration. \label{figure:correlation_match} }

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/random_large_correlation_selected_models.pdf}
\hspace{5mm}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/random_full_correlation_selected_models.pdf}
\end{center} 
\caption{ mean ACFs   and their correponding standard deviation (error bars)  of some selected models in different mass ranges
over the 7 subfields of the SSA22 field (left) and the entire 12 field sample (rigth) using the
random configuration. \label{figure:correlation_random} }
